Competing Bandits: The Perils of Exploration under Competition

### 2018-09-03 paper/content/barriers.tex
edits

\begin{finding}
\textit{Maintaining either the data or reputation advantage alone still allows the incumbent to retain a significant portion of the market. \swcomment{too vague. what does significant mean?}\\ \indent When the incumbent plays $\TS$, the data advantage serves as a larger barrier to entry compared to reputation, but when the incumbent plays $\DEG$ or $\DG$ there is no substantial difference between the two.}
\end{finding}

>>>>

\begin{finding}
\textit{Maintaining either the data or reputation advantage alone still allows the incumbent to retain a significant portion of the market. \swcomment{too vague. what does significant mean?}\\ \indent When the incumbent plays $\TS$, the data advantage serves as a larger barrier to entry compared to reputation, but when the incumbent plays $\DEG$ or $\DG$ there is no substantial difference between the two barriers.}
\end{finding}

### 2018-09-03 paper/content/inverted_u.tex
edits

\documentclass[../competing_bandits.tex]{subfiles}
\begin{document}
\section{Competition vs Better Algorithms: Inverted-U}\label{section:5}
 Now we demonstrate the inverted-U relationship between the incentivized
  algorithms and the competition levels. In particular, we investigate
  the incentivized algorithms under three different regimes: permanent
  monopoly, temporary monopoly, and permanent duopoly. \gaedit{We break indifference between exploration algorithms and non-exploration algorithms towards non-exploration algorithms due to deployment costs.} \gadelete{First, the story for permanent monopoly is relatively straightforward.}
 We summarize the relationship between the different competition levels and incentivized algorithms as follows:

\begin{conjecture}\label{conj:inverted-u}
\textit{For sufficiently low warm start,
 the optimal strategies in the competition game are:
\begin{center}
\textbf{Permanent Monopoly} - $\DG$ \\
\textbf{Temporary Monopoly} - $\TS$ \\
\textbf{Permanent Duopoly} - $\DG$ \\
\end{center}
The conditions on $\TS$ being dominant under the temporary monopoly are that the incumbent is a temporary monopoly for sufficiently many periods.
}
\end{conjecture}

\xhdr{Permanent Monopoly.} Since there is only a single firm
  in the market for the entire period, the firm can take the entire
  market regardless what algorithm it deploys. \gadelete{Assuming the deployment of any exploration algorithms will incur certain cost} \gaedit{Since we break indifferences by supposing the firm prefers easier to deploy algorithms}, the firm would choose to deploy $\DG$.

@@

\xhdr{Permanent Duopoly} Permanent duopoly corresponds to the model described in section 2 where $X = 0$ so that both firms enter the market simultaneously. What algorithms are firms incentivized to deploy? We report the average market share taken over the $N$ simulations for a set of exogenous values of $T_0$. Additionally, we report the mean and median of the effective end of game.

Since both firms enter at the same time the game is symmetric and the competition game is zero-sum so we only need to compute the expected payoffs of three pairs of strategies. We do not report them in the figures, but when both firms play the same algorithm the expected market share is 50/50. Since our results are from simulations, we interpret algorithm $A$ being better than algorithm $B$ if the resulting average market share of $A$ is statistically greater than $0.5$. Otherwise, the firm is indifferent between $A$ and $B$ with ties broken towards algorithms that are easier to deploy.

>>>>

\documentclass[../competing_bandits.tex]{subfiles}
\begin{document}
\section{Competition vs Better Algorithms: Inverted-U}\label{section:5}
Now we demonstrate the inverted-U relationship between the
incentivized algorithms and the competition levels. In particular, we
investigate the incentivized algorithms under three different regimes:
permanent monopoly, temporary monopoly, and permanent duopoly:
\swdelete{We break indifference between exploration algorithms and
  non-exploration algorithms towards non-exploration algorithms due to
  deployment costs.}  \swdelete{We summarize the relationship between
  the different competition levels and incentivized algorithms as
  follows:} \swcomment{deleted the discussion of tie-breaking since it
  feels out of place.}
\begin{finding}\label{conj:inverted-u}
  \textit{For sufficiently low warm start, the optimal strategies
    \swcomment{for whom??} in the competition game are:
\begin{center}
\textbf{Permanent Monopoly} - $\DG$ \\
\textbf{Temporary Monopoly} - $\TS$ \\
\textbf{Permanent Duopoly} - $\DG$ \\
\end{center}
The conditions on $\TS$ being dominant under the temporary monopoly are that the incumbent is a temporary monopoly for sufficiently many periods.\swcomment{vague here. }
}
\end{finding}

\xhdr{Permanent Monopoly.} Since there is only a single firm in the
market for the entire period, the firm can take the entire market
regardless what algorithm it deploys. \gadelete{Assuming the
  deployment of any exploration algorithms will incur certain cost}
\swedit{Since we assume that exploration algorithms ($\DEG$ and $\TS$)
  would incur deployment cost}, the firm would choose to deploy $\DG$.

@@

\xhdr{Permanent Duopoly} \swdelete{Permanent duopoly corresponds to the model
described in section 2 where $X = 0$ so that both firms enter the
market simultaneously. What algorithms are firms incentivized to
deploy? We report the average market share taken over the $N$
simulations for a set of exogenous values of $T_0$. Additionally, we
report the mean and median of the effective end of game.}
\swedit{

  Since in this case both firms enter at the same time, they will both
  get an expected market share of $1/2$ whenever they deploy the same
  algorithms.

To see what algorithms are the firms incentivized to deploy, we look at the average market
share taken over the $N$ simulations for different values of warm-up length $T_0$.

}

\swdelete{Since both firms enter at the same time the game is symmetric and the competition game is zero-sum so we only need to compute the expected payoffs of three pairs of strategies. We do not report them in the figures, but when both firms play the same algorithm the expected market share is 50/50. Since our results are from simulations, we interpret algorithm $A$ being better than algorithm $B$ if the resulting average market share of $A$ is statistically greater than $0.5$. Otherwise, the firm is indifferent between $A$ and $B$ with ties broken towards algorithms that are easier to deploy.}
